 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-04-30 paper.Rmd
update details here
add some tour details

@@

>>>>

synthesis of some other techniques like LLE, Isomap and PHATE

@@

Recall our $n \times p$ data matrix $X$

A tour is sequence of $p \times d$ orthonormal projection matrices (bases) $A_{t \in \mathbb{N}}$, where $d$ is typically $1$ or $2$.

A tour allows us to explore the set of all $d$-dimensional subspaces via the projection of $X$ onto $A$. 
]

---

# How does it work?

.large[
We visualise the sequence of low dimensional projections:

$$Y_{t} = XA_{t}$$

as animated scatter or density plots. 
]

---

.large[**Grand Tour:** generate a set of random orthnormal bases, interpolate between them.]

```{r basis-view, out.width="50%", echo = FALSE}
include_graphics("img/bases-generation.png")
```

(From _Buja, Cook, Asimov and Hurley, 2004_)
---

class: middle

.large[The tour is enhanced by **interactivity**:

- play/pause the current projection
- zooming to find 'interesting' points
- highlighting sets of points
- linking multiple views
